A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
debug the compile error - fixed the lables

### The Predicted Proportion of Support a Candidate Received in a Poll (%)

The main variable we aim to forecast is the pct variable, which represents the proportion of the vote a candidate received in a poll.@tbl-pct_cleaned and @fig-pct_cleaned shows the summary statistics and distribution of pct variable in a filtered dataset that only comprises of votes from relatively high-quality polling organizations. We also get the popular vote predictions for each candidate using the predict() function and add this to the dataset as the predicted_pct variable. We have showed the summary statistics and distribution for predicted_pct in @tbl-pct_predicted and @fig-pct_predicted, respectively.

Comparing our predictions to the data, our predictions have a smaller range than the cleaned data. While the difference in mean is 2\'%' lower for our prediction than our cleaned data. The results suggest there is less variation in our predictions than the cleaned dataset.

```{r}
#| label: tbl-pct_cleaned
#| fig-cap: Summary statistics for the proportion of support candidates received in the poll
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'pct' variable
summary_stats <- cleaned_president_polls %>%
  summarize(
    mean = round(mean(pct, na.rm = TRUE), 2),
    median = round(median(pct, na.rm = TRUE), 2),
    min = round(min(pct, na.rm = TRUE), 2),
    max = round(max(pct, na.rm = TRUE), 2), 
    sd = round(sd(pct, na.rm = TRUE), 2), 
    n = n()

@@

```{r}
#| label: fig-pct_cleaned
#| fig-cap: Distribution of the proportion of support candidates received in the poll
#| echo: false

@@

```{r}
#| label: tbl-pct_predicted
#| fig-cap: Summary statistics for the predicted proportion of support candidates received in the poll
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

@@

```{r}
#| label: fig-pct_predicted
#| fig-cap: Distribution of the predicted proportion of support candidates received in the poll
#| echo: false
#| fig-width: 5 
#| fig-align: center

>>>>

### The Predicted Proportion of Support a Candidate Received in a Poll

The main variable we aim to forecast is the pct variable, which represents the proportion of the vote a candidate received in a poll.@tbl-pct-cleaned and @fig-pct-cleaned shows the summary statistics and distribution of pct variable in a filtered dataset that only comprises of votes from relatively high-quality polling organizations. We also get the popular vote predictions for each candidate using the predict() function and add this to the dataset as the predicted_pct variable. We have showed the summary statistics and distribution for predicted_pct in @tbl-pct-predicted and @fig-pct-predicted, respectively.

Comparing our predictions to the data, our predictions have a smaller range than the cleaned data. While the difference in mean is 2% lower for our prediction than our cleaned data. The results suggest there is less variation in our predictions than the cleaned dataset.

```{r}
#| label: tbl-pct-cleaned
#| tbl-cap: Summary statistics for the proportion of support candidates received in the poll
#| echo: false
#| message: false
#| warning: false
#| tbl-align: center
#| tbl-width: 82%

summary_stats <- cleaned_president_polls %>%
  summarize(
    mean = round(mean(pct, na.rm = TRUE), 2),
    median = round(median(pct, na.rm = TRUE), 2),
    min = round(min(pct, na.rm = TRUE), 2),
    max = round(max(pct, na.rm = TRUE), 2), 
    sd = round(sd(pct, na.rm = TRUE), 2), 
    n = n()
  )

summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

@@

```{r}
#| label: fig-pct-cleaned
#| fig-cap: Distribution of the proportion of support candidates received in the poll
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: tbl-pct-predicted
#| tbl-cap: Summary statistics for the predicted proportion of support candidates received in the poll
#| echo: false
#| message: false
#| warning: false
#| tbl-align: center
#| tbl-width: 82%

@@

```{r}
#| label: fig-pct-predicted
#| fig-cap: Distribution of the predicted proportion of support candidates received in the poll
#| echo: false
#| message: false
#| warning: false
#| fig-width: 5 
#| fig-align: center
